%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{fontawesome5}
\usepackage{tabularx}
\usepackage{comment}
\usepackage{ragged2e}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{tikzpagenodes}
\usepackage{calc}
\usepackage[super]{nth}
\newcommand*{\ClipSep}{0.4cm}%
\usetikzlibrary{calc} 
\usepackage[absolute,overlay]{textpos}
\usepackage[
top    =3.3cm,
bottom = 2cm,
left   = 1.9cm,
right  = 1.9cm]{geometry}

\usepackage{multicol}
\usepackage{import}

% personal data
\name{Maurice D.}{Hanisch}
\address{Gubelstrasse 44}{Zurich}{Switzerland}% optional, remove / comment the line if not 
  
\newcommand*{\customcventry}[5][.5em]{
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     { #3}
  \end{tabular} \\
  \begin{tabular}{@{}l} 
    {\itshape\small #4}
  \end{tabular}
  \ifx&#5&%
  \else{\\%
    \begin{minipage}{0.82\maincolumnwidth}%
      \small#5%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\customcvproject}[4][.25em]{
%   \vfill\noindent
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     { #3}
  \end{tabular}
  \ifx&#4&%
  \else{\\%
    \begin{minipage}{0.82\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{#1}}
  
\newcommand*{\custompublication}[2][0.6em]{
    \begin{minipage}{\maincolumnwidth}%
       #2%
    \end{minipage}
  \par\addvspace{#1}}

\setlength{\tabcolsep}{12pt}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\begin{textblock*}{14cm}(3.7cm,1.5cm) % {block width} (coords) 
    \makecvtitle
\end{textblock*}
\begin{textblock*}{15cm}(2.8cm,2.5cm)
\begin{center}
\begin{tabular}{ c c }
 \faEnvelope\enspace mhaniscn@student.ethz.ch  & \faMobile\enspace \quad +41 763 61 91 83 \\
\end{tabular}
\end{center}
\end{textblock*}
\begin{textblock*}{15cm}(2.8cm,2.9cm)
\begin{center}
\begin{tabular}{ c c }
 \faLinkedin\enspace \href{https://www.linkedin.com/in/mauricehanisch/}{\underline{www.linkedin.com/in/mauricehanisch/}} & \faGithub\enspace\href{https://github.com/MauriceDHanisch/}{\underline{www.github.com/MauriceDHanisch/}}\\
\end{tabular}
\end{center}
\end{textblock*}

\vspace*{0mm}

\section{Education}
\customcventry{M.Sc. Physics}{09/2022 -- Present}{ETH Zurich, Switzerland}
{\begin{itemize}
    \item Current GPA: 5.61/6.00 (CH)
    \item Focus: Q. Error Correction, Q. Information Processing, Machine Learning
    \item Selected past \& current coursework: Advanced Q. Algorithms, Probabilistic Artificial Intelligence, Q. Error Correction, Q. Information Processing 1 \& 2, Trapped Ions.
\end{itemize}
}
\vspace{-0.1cm}
{\textit{| Partly financed by the \underline{Rayer scholarship} | Dr. Mas-Fraissinet, France.}}
\vspace{0.3cm}

\customcventry{B.Sc. Physics}{10/2018 -- 09/2022}{LMU Munich, Germany}
{\begin{itemize}
  \item GPA: 1.28/1.00 (DE). Theoretical physics electives.
\end{itemize}
}
\vspace{-0.1cm}
{\textit{| Mainly financed by the \underline{Rayer scholarship} | Dr. Mas-Fraissinet, France.}}
\vspace{0.3cm}

\customcventry{Medical Degree}{10/2017 -- 02/2018}{LMU Munich, Germany}
{\begin{itemize}
  \item GPA: N/A. Not completed.
\end{itemize}
}

\customcventry{Baccalauréat}{09/2014 -- 07/2017}{Lycée Sud des Landes, St-Vincent-de-Tyrosse, France}
{\begin{itemize}
    \item GPA 16.00/20.00 (FR). Graduated with the highest possible honors at the age of 16.
\end{itemize}
}

\section{Research Experience}
\customcventry{Master's Thesis}{09/2023 -- Present}{IBM Quantum, Zurich, Switzerland}
{\begin{itemize}
  \item 
  \item 
  \item 
  \item Supervisors: Dr. James Wootton, Dr. Joseph Renes
\end{itemize}
}

\customcventry{Semester Project}{08/2022 -- 10/2022}{ETH Zurich, Switzerland}
% {\scriptsize \href{https://ethz.ch/content/dam/ethz/special-interest/phys/quantum-electronics/tiqi-dam/documents/semester_theses/smesterthesis_Maurice_Hanisch}{\underline{\faLink ~Report Link}}}
% \vspace{-0.1cm}
{\begin{itemize}
    \item “Towards a tunable beamsplitter interaction between two GKP-encoded qubits”
    \item Experimental project on the motional interaction of GKP-encoded qubits in trapped ions.
    \item Designing and simulation of trapping potentials and then experimental testing of the found potentials.
    \item Skills: Python, Hardware: ion trapping. 
    \item Supervisor: Prof. Jonathan Home    
\end{itemize}}
\vspace{0.2 cm}

\customcventry{Bachelor's Thesis}{04/2022 -- 09/2022}{Max-Planck-Institute for Quantum Optics, Munich, Germany}
{\begin{itemize}
    \item “Space-efficient quantum computation of fermionic and bosonic Gaussian systems”
    \item Introduction to various theoretical research areas (entanglement simulation with Python, entropic uncertainty principles, tensor networks) by Dr. Adrian Rubio.
    \item Investigating the computational advantages in terms of time and space of fermionic and bosonic Gaussian circuits.
    \item
    \item Supervisors: Prof. Ignacio Cirac, Dr. Adrian Rubio.
\end{itemize}}

\section{Teaching}
\customcventry{Teaching Assistant in Analysis I}{09/2023 -- Present}{ETH Zürich, Zurich, Switzerland}
{\begin{itemize}
  \item Teaching calculus for over 60 \nth{1} year mechanical engineering students
  \item Lecturer: Dr. Andreas Steiger, Dr. Fabian Ziltener
\end{itemize}
}

\customcventry{Student Assistant in Experimental Methods for Engineers}{09/2021 -- 01/2022}{ETH Zürich, Zurich, Switzerland}
{\begin{itemize}
    \item Taught basics of particle imaging velocimetry (PIV) \& tracking velocimetry (PTV) data collection and processings
\end{itemize}
}

\customcventry{Teaching Assistant in Physics III}{09/2020 -- 12/2020}{ETH Zürich, Zurich, Switzerland}
{\begin{itemize}
    \item Taught the basics of quantum mechanics in a weekly in-person class for 25 \nth{2} year B.Sc. Physics students with remote students over Zoom
    \item Lecturer: Prof. Yiwen Chu
\end{itemize}}

\section{Work Experience}


\section{Competitions}
\customcventry{Quandela LOQCathon 2.0}{11/2023}{Sorbonne Université, Paris, France}
{\begin{itemize}
    \item Won 1st Prize of the competetion (3000€). Worked on Électricité de France (EDF) challenge on quantum reservoir computing using Linear Optics for time series prediction
\end{itemize}}
\customcventry{Quantum Hackathon}{05/2023}{ETH Zürich, Zurich, Switzerland}
{\begin{itemize}
    \item Worked on Moody's Analytics challenge using quantum Monte Carlo simulations for option pricing
\end{itemize}}


\section{Extracurricular Acitivities}
\customcventry{Hack4Good Organizer}{09/2023 -- Present}{Analytics Club ETH Zürich (ACE), Zurich, Switzerland}
{\begin{itemize}
  \item Project coordinator for the project provided by WWF on using LLMs for sentiment analysis
  \item Organizing workshops on "Data science for NGOs" for the participants
\end{itemize}
}

\customcventry{Board Member $|$ Studies}{03/2023 -- Present}{Quantum Engineering Commission (QEC), Zurich, Switzerland}
{\begin{itemize}
    \item Responsible for the Quantum Engineering MSc mentoring program, Alumni \& internship statistics as well as study documents
    \item Built a pipeline for automated exam protocol \& course review creation using Python, Google API, and LaTeX
\end{itemize}}

\customcventry{Student Mentor}{09/2021 -- 02/2022}{ETH Physics Department Student Mentoring}
{\begin{itemize}
    \item Mentor for a group of three first-year BSc students including regular meetings to discuss their study progress
\end{itemize}}

\section{Technical Skills and Interests}
% TO DO: Python libraries aufzählen
\textbf{Technical:} Python, MATLAB, C++, LTspice, LaTeX, MS Office, Autodesk Fusion 360, ANSYS Maxwell  
\\
\textbf{Languages:} German (native), English (C1), French (B2)
\\
\textbf{Interests:} Calisthenics, Glider flying (AFG Zürich), Bouldering, Swimming, Cycling




\end{document}





